Behavior Driven Development in Haskell

### 2012-05-25 paper.tex
Wording of section on "Haddock"

As we described, Haddock version 2.7.2 or earlier has
the markup for code block but does not provide
markups for examples and properties.
We implemented a markup for examples ({\tt >>>}) and 
it is available in Haddock version 2.8 or later.
We also extended Haddock to support a markup for
properties ({\tt prop>})
which will be available in the future release.
Both examples and properties in Haddock markup are pretty printed when producing document
such as in HTML.

>>>>

As we described, Haddock version 2.7.2 or earlier provides markup syntax for
code blocks, but does not provide any markup syntax for examples or properties.
We implemented markup support for examples ({\tt >>>}) and it is available in
Haddock version 2.8 or later.
We also extended Haddock to support markup for properties ({\tt prop>}) which
will be available with a future release of Haddock.
Both examples and properties in Haddock comments are pretty-printed when
generating documentation, (e.g. as HTML).
